---
title: "Title"
subtitle: "Subtitle"
output:
    powerpoint_presentation:
        slide_level: 3
        reference_doc: "learning_team_presentation_style_reference.pptx"
---


```{r setup, echo = FALSE, cache = FALSE}
knitr::opts_knit$set(eval.after = 'fig.cap')
knitr::opts_chunk$set(echo = FALSE)
knitr::read_chunk('learning_team_presentation_analysis.R')
```


# Section Header (Slide 1)


## Section Header (Slide 2)


### Title (Slide 3)

Content


### Title (Slide 4)

- a
- nested
    - bulleted
    - list
        - is
        - good
- now


### Title (Slide 5)

Content

::: notes

A note

:::


### Title (Slide 6)

:::::: {.columns}

::: {.column}

Column 1

:::

::: {.column}

Column 2

:::

::::::


### Title (Slide 7)

```{r example, echo=FALSE, fig.cap=caption, fig.width = 10, fig.height = 5, dpi = 600}
caption <- 'a caption!'
plot(rnorm(100))
```

### Title (Slide 8)

*italic*
**bold**
~~strikeout~~
~subscript~
^superscript^
[small caps]{.smallcaps}
`verbatim`

> Block quote


### Title (Slide 9)

:::::: {.columns}

::: {.column}

```{r, echo=FALSE, fig.cap=caption, fig.width = 5, fig.height = 6, dpi = 600}
caption <- 'a caption!'
plot(rnorm(100))
```
:::

::: {.column}

#### Content Header

##### Smaller Header

###### Smallest Header

stuff

:::

::::::


### Title (Slide 10)

one two three four five
--- --- ----- ---  ----
a   1   2     3    4
b   1   2     3    4


### Title (Slide 11)

```{r, echo=FALSE}
knitr::kable(head(mtcars, 3)[, 2:5])
```


### Title (Slide 12)

:::::: {.columns}

::: {.column}

Column 1

:::

::: {.column}

```{r, echo=FALSE}
knitr::kable(head(mtcars, 3)[, 2:5])
```

:::

::::::

