---
title: "Grant & Longstreet"
subtitle: "An\nOpposing\nFriendship"
output:
    powerpoint_presentation:
        slide_level: 2
        reference_doc: "learning_team_presentation_style_reference.pptx"
---


```{r setup, echo = FALSE, cache = FALSE}
knitr::opts_knit$set(eval.after = 'fig.cap')
knitr::opts_chunk$set(echo = FALSE)
knitr::read_chunk('learning_team_presentation_analysis.R')
```


```{r analysis}
<<load_analysis_packages>>
<<load_stopwords>>
<<read_and_preprocess_text>>
<<extract_chapters>>
<<extract_paragraphs>>
<<extract_sentences>>
<<extract_tokens>>
<<token_counts>>
<<extract_hapax>>
<<type_token_ratio>>
<<tf_idf>>
<<token_frequencies>>
<<positional_token_frequencies>>
<<token_correlations>>
<<summary_statistics>>
```


```{r plots}
<<load_graphics_packages>>
<<declare_fonts>>
<<load_and_check_system_fonts>>
<<load_and_check_windows_fonts>>
<<declare_colors>>
<<declare_desaturation_function>>
<<create_freq_plots>>
<<create_zipf_plots>>
<<create_ttr_plots>>
<<create_stats_plots>>
<<create_sentiment_plot>>
<<create_correlation_plot>>
```

## Texts

###### *Personal Memoirs of U. S. Grant*

- Ulysses S. Grant

###### *From Manassas to Appomattox: Memoirs of the Civil War in America*

- by James Longstreet


## Topics

- Summary Statistics
- Frequency Analysis
- Correlation Analysis
- Type-Token Ratio
- Hapax Richness
- Sentiment Analysis


# Summary Statistics


## Sentence Lengths


```{r senlen, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
sentence_lengths
```


# Frequency Analysis


## Word Frequency

```{r word_freq_plot, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
word_freq_plots
```


## Bigram Frequency

```{r bigram_freq_plot, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
bigram_freq_plots
```


## Trigram Frequency

```{r trigram_freq_plot, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
trigram_freq_plots
```

## Punctuation Frequency

```{r punct_freq_plot, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
punct_freq_plots
```


## Words Starting Sentences

```{r bsent_freq1, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
word_starting_sentence_freqs_plots
```


## Bigrams Starting Sentences

```{r bsent_freq2, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
bigram_starting_sentence_freqs_plots
```


## Trigrams Starting Sentences
```{r bsent_freq3, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
trigram_starting_sentence_freqs_plots
```


## Words Ending Sentences

```{r esent_freq1, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
word_ending_sentence_freqs_plots
```


## Bigrams Ending Sentences

```{r esent_freq2, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
bigram_ending_sentence_freqs_plots
```


## Trigrams Ending Sentences
```{r esent_freq3, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
trigram_ending_sentence_freqs_plots
```


# Correlation Analysis


## Word Correlations
```{r corr1, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
correlation_plot
```


# Type-Token Ratio


## Type-Token Ratio
```{r ttr, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
ttr_plot
```

# Hapax Richness


## Zipf's Law
```{r zipf, fig.width=10, fig.height=5, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
zipf_plots
```

# Sentiment Analysis


## Sentiments by Chapter

```{r sent, fig.width=8, fig.height=4, dpi=600, fig.cap=caption}
caption <- 'Dummy caption'
sentiment_plot
```


# Questions
